Software Citation Principles

### 2016-07-24 sc-principles/software-citation-principles.tex
copying desription for B.9 from the Google Doc
adding a little to B.14 and declaring it sufficiently done
adding description to B.16

\niemnote{add description}

@@

This use case is similar to ``Repository showing scientific impact of holdings'',
where a funder wants to find out the use and impact and software that they
supported.

steps/requirements\niemnote{add more to this?}

@@

\niemnote{add description?}

>>>>

Requirements
\begin{itemize}
\item Name of software
\item Names of software authors/contributors
\item Location/repository
\item Citable DOI of software
\item Format for citing software in JATS, for example, as well as references in the text itself
\end{itemize}

@@

This use case is similar to ``Repository showing scientific impact of holdings'',
where a funder wants to find out the use and impact and software that they
supported.  It is also similar to ``Researcher who wants to know who uses the researcher's software.''

@@

Reference management systems may need to be updated to internally understand that their is a software reference type, and to be able to output references to software in common formats.
